Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-27 paper/main.tex
fix title

\title{Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems}
% Double-blind
\author{Double-blind}
% \author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
% \institute{
%    Basque Center for Applied Mathematics\\
%    \email{eirurozki@bcamath.org}
%    \and
%    University of Málaga, Málaga, Spain\\
%    \email{manuel.lopez-ibanez@uma.es}
% }
\date{}%

@@

Although we were inspired by previous work on ACO for expensive black-box
combinatorial problems~\citep{PerLopStu2015si}, UMM is, to the best of our
knowledge, the first EDA specifically designed for such problems that is able
to obtain competitive\EKHINE{hhmmm lo hacemos mejor o igual} results when compared with Bayesian optimizers. The
results presented here show that, despite the intrinsic difficulty of this scenario, there are still significant advances yet to be made. Thus, we hope
that this paper will motivate further research. % on such problems.

>>>>

\title{Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems}
\titlerunning{Unbalanced Mallows Models for Expensive Black-Box Permutation Problems}
% Double-blind
\author{Double-blind}
% \author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
% \institute{
%    Basque Center for Applied Mathematics\\
%    \email{eirurozki@bcamath.org}
%    \and
%    University of Málaga, Málaga, Spain\\
%    \email{manuel.lopez-ibanez@uma.es}
% }
\date{}%

@@

Although we were inspired by previous work on ACO for expensive black-box
combinatorial problems~\citep{PerLopStu2015si}, UMM is, to the best of our
knowledge, the first EDA specifically designed for such problems that is able
to match (and sometimes even improve) the results of a Bayesian optimizer\EKHINE{hhmmm lo hacemos mejor o igual}. The
results presented here show that, despite the intrinsic difficulty of this scenario, there are still significant advances yet to be made. Thus, we hope
that this paper will motivate further research. % on such problems.
